
\begin{abstract}
  \markboth{\abstractname}{}

% Make first version of abstract consist of four sentences. Fill in
% more later, if needed.

% First sentence: state the problem.

% Second sentence: describe why this is a problem.

% Third sentence: state your solution.

% Fourth sentence: sketch the consequences of your solution
\com{
\todo[inline]{Keep in mind that most of your potential readers are only going to read your title and abstract. This is why it is important that the abstract give them enough information that they can decide is this document relevant to them or not. Otherwise the likely default choice is to ignore the rest of your document.\\
A abstract should stand on its own, i.e., no citations, cross references to the body of the document, acronyms must be spelled out, …\\
Write this early and revise as necessary. This will help keep you focused on what you are trying to do.}

Write an abstract\todo{Use about 1/2 A4-page (250 and 350 words).}  with the following components:
\begin{itemize}
  \item What is the topic area? (optional) Introduces the subject area for the project.
  \item Short problem statement
  \item Why was this problem worth a Master’s thesis project? (i.e., why is the problem both significant and of a suitable degree of difficulty for a Master’s thesis project? Why has no one else solved it yet?)
  \item How did you solve the problem? What was your method/insight?
  \item Results/Conclusions/Consequences/Impact: What are your key results/conclusions? What will others do based upon your results? What can be done now that you have finished - that could not be done before your thesis project was completed?\todo[inline]{The presentation of the results should be the main part of the abstract.}
\end{itemize}
}

\noindent
% State the problem.
Autonomous lawn mowers have been available to consumers for more than $20$ years.
During this period, advancements in embedded device computations and sensor performance have led to improvements in the reliability of these robots. 
Despite recent improvements, the opportunity for further innovation of such systems remains significant. 
% hi buddy this doesn't make sense to me but put it back in if you want Despite this, little effort has been spent on their innovation and evolution related to the development of new features.

% Why is this a problem?
Currently, many autonomous robots rely on electric wires installed underground to delimit the boundaries of the lawn. %, to which they react without reasoning.
Such a configuration is simple, but more effective autonomous solutions are available.

% state your solution.
This thesis focuses on %employing currently available techniques to design the core modules needed to advance the capabilities of these systems. % (this sentence is not saying much, it's pretty general... what are you actually doing? i.e. designs a kalman filter to do xyz)
the analysis and related implementation of both localisation and mapping features for autonomous lawn mowers. % are presented.
Heterogeneous sensors and their different configurations are investigated and an Adaptive Extended Kalman Filter is proposed to fuse their measurements.
This technique improves the pose estimation of the autonomous lawn mower, which is then exploited by the mapping module.
%The chosen approach for the latter, b
Based on Bayesian's inference, the mapping module updates the knowledge of the map based on direct interactions with the environment.

% sketch the consequences of your solution
The final results highlight the importance of precise localisation as the bottleneck for the development of new features.
The improved pose estimation enables the employment of a virtual boundary, but it is not accurate enough to precisely map the presence of objects in the environment.
Advanced features which could be developed from the proposed configuration are related to deterministic coverage algorithms and the interaction with lawn objects.


\subsection*{Keywords}
\noindent
Autonomous Mobile Robot, Sensor Fusion, Localisation, Mapping


\com{
\todo[inline]{Choosing good keywords can help others to locate your paper, thesis, dissertation, … and related work.}

Choose the most specific keyword from those used in your domain, see for example:
ACM's Computing Classification System (2012) or
(2014) IEEE Taxonomy.

Mechanics:
\begin{itemize}
  \item The first letter of a keyword should be set with a capital letter and proper names should be capitalized as usual.
  \item Spell out acronyms and abbreviations.
  \item Avoid "stop words" - as they generally carry little or no information.
  \item List your keywords separated by commas (",").
\end{itemize}
Since you should have both English and Swedish keywords - you might think of ordering them in corresponding order (i.e., so that the nth word in each list correspond) - thus it would be easier to mechanically find matching keywords.
}

\end{abstract}


%\cleardoublepage
\clearpage
