
\section*{Acknowledgments }
\markboth{Acknowledgments}{}
\com{
\todo[inline]{It is nice to acknowledge the people that have helped you. It is
  also necessary to acknowledge any special permissions that you have gotten –
  for example getting permission from the copyright owner to reproduce a
  figure. In this case you should acknowledge them and this permission here
  and in the figure’s caption. \\
  Note: If you do not have the copyright owner’s permission, then you cannot use any copyrighted figures/tables/… .
}
}
%I would like to thank xxxx for having yyyy.\\


\noindent I would like to thank Thiemo Voigt and Joakim Eriksson for the opportunity to work on this challenging topic with RISE.
Their ideas and recommendations helped define the purpose of the thesis, and their positiveness enabled its accomplishment.

I am grateful to Håkan Carlsson for the supervision of the project.
His insights and support have been vital for the development of this thesis.
I was glad to choose him as a supervisor for his friendly and down-to-earth assistance.

I wish to thank Haibo Li for the examination of the thesis.
I truly appreciated the promptness and availability he has demonstrated from the beginning to the end of this project.

I would also like to mention my appreciation to the Husqvarna team and Mikael Alexiusson for their availability.
I am thankful for the opportunity to present my project to them and gain valuable insights in return.

I need to acknowledge my family for the continuous help and support which enabled me to reach this moment.
I have tried to compensate for the encouragement they provided through the whole process and I hope to have made them as proud of me as I am grateful to them.

Finally, I want to express my gratitude to my friends, as their moral support allowed me to achieve more than I could possibly fathom. 

% and to my perfect girlfriend for being so cool and just so so cool xoxoxo jess is the best 
\acknowlegmentssignature
